Title Goes Here

### 2020-04-21 analysis/paper/paper.Rmd
correlation for site

# correlation for all
cplotall <- corrplot(SCOR, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
# for phase 2
cplot2 <- corrplot(cor2, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
# for phase 3
cplot3 <- corrplot(cor3, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

@@

@@

#simpler way to calculate Correlataion, you can use
cor(SYG6_DF)

@@

@@

SYG6_PCA <- prcomp(SYG6_DF, center = TRUE, scale = TRUE)

@@

#simpler way to calculate Correlataion, you can use
cor(SYG_1DF)

@@

@@

#simpler way to calculate Correlataion, you can use
cor(SYG_4DF)

@@

@@

>>>>

par(mfrow=c(1,3))
# correlation for all
cplotall <- corrplot(SCOR, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
# for phase 2
cplot2 <- corrplot(cor2, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
# for phase 3
cplot3 <- corrplot(cor3, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

@@

par(mfrow=c(2,1)) #doesn't work

ACOR2 <- pairs(cor2)
ACOR3 <- pairs(cor3)

@@

#simpler way to calculate Correlataion, you can use
SYG6_cor <- cor(SYG6_DF)

@@

cplot_SYG6 <- corrplot(SYG6_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

@@

SYG6_PCA <- prcomp(SYG6_cor, center = TRUE, scale = TRUE)

@@

#simpler way to calculate Correlataion, you can use
SYG_1cor <- cor(SYG_1DF)

@@

cplot_SYG_1 <- corrplot(SYG_1cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

SYG6_PCA <- prcomp(SYG6_cor, center = TRUE, scale = TRUE)

@@

#simpler way to calculate Correlataion, you can use
SYG_4cor <- cor(SYG_4DF)

@@

cplot_SYG_4 <- corrplot(SYG_4cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

@@

Correlations for each site
```{r}
par(mfrow=c(1,3))
cplot_SYG6 <- corrplot(SYG6_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
cplot_SYG_1 <- corrplot(SYG_1cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
cplot_SYG_4 <- corrplot(SYG_4cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```
